---
title: "ds-ac101"
output:
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r}
library(knitr)
library(dplyr)
library(ggpubr)
library(kableExtra)
library(rmarkdown)
library(stringr)
```

# Group

```{r}
load("USERS.RData")
USERS$NOME <- str_split(as.character(USERS$NAME), " ", simplify = TRUE)[,1]
USERS$COGNOME <- str_split(as.character(USERS$NAME), " ", n=2, simplify = TRUE)[,2]
USERS$POS[17]<-"external"
```

```{r}
grp = "ds-ac101"
usrs = filter(USERS, GROUP == grp) %>% 
  select("COGNOME","NOME","ID", "ROLE","POS") %>%
  arrange(ROLE, COGNOME)
kable(usrs, row.names=F)
```

# Projects

1. Multi-information source Bayesian optimization via Augmented Gaussian Processes

    | | |
    |-|---|
    | PI | Antonio Candelieri |
    | TYPE | Research |
    | KEYWORDS | Multi Information Source Optimization, Bayesian Optimization, Gaussian Processes |
    | START/END | 2020-02-01 - ongoing |
    | OUTPUT | A paper under review, submitted to ICANN 2020 ([29th International Conference on Artificial Neural Networks](https://e-nns.org/icann2020/)): Candelieri A., Archetti F., Ponti A., Perego R. "Energy Efficient Hyperparameters tuning through Augmented Gaussian Processes and Multi-information Source Optimization" |

2. Automated Tiny Machine Learning

    | | |
    |-|---|
    | PI | Antonio Candelieri |
    | TYPE | Research |
    | KEYWORDS | Automated Machine Learning, Tiny Machine Learning, Bayesian Optimization under unknown constraints |
    | START/END | 2020-03-01 - ongoing |
    | OUTPUT | A paper under review, submitted to the Special Issue "Automation in AI and Machine Learning", in IEEE Transactions on Pattern Analysis and Machine Intelligence (TPAMI, [CfP](https://ccc.inaoep.mx/~hugojair/pmwiki/index.php?n=Main.SpecialIssueOnAutoMLAtTPAMI)): Perego R., Candelieri A., Archetti F., Pau D., "AutoTinyML for microcontrollers: dealing with black-box deployability" |

3. Composition of kernel and acquisition functions for High Dimensional Bayesian Optimization

    | | |
    |-|---|
    | PI | Antonio Candelieri |
    | TYPE | Research |
    | KEYWORDS | Bayesian Optimization, High-Dimensionality, Kernel composition |
    | START/END | 2020-12-01 - ongoing |
    | OUTPUT | A paper accepted to LION 14 (the 14th Learning and Intelligent Optimization Conference): Candelieri A., Giordani I., Perego R., Archetti F. "Composition of kernel and acquisition functions for High Dimensional Bayesian Optimization" |

4. Learning Optimal Control of Water Distribution Networks through Sequential Model-based Optimization

    | | |
    |-|---|
    | PI | Antonio Candelieri |
    | TYPE | Research |
    | KEYWORDS |  |
    | START/END | 2020-12-01 - ongoing |
    | OUTPUT | A paper accepted to LION 14 (the 14th Learning and Intelligent Optimization Conference): Candelieri A., Galuzzi B., Giordani I, Archetti F. "Learning Optimal Control of Water Distribution Networks through Sequential Model-based Optimization" |