---
title: "ds-ac101"
output:
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r}
library(knitr)
library(dplyr)
library(ggpubr)
library(kableExtra)
library(rmarkdown)
library(stringr)
```

# Team

```{r}
USERS <- read.csv("/Users/aldosolari/Documents/mygithub/datalab/Users.csv")
USERS$NOME <- str_split(as.character(USERS$NAME), " ", simplify = TRUE)[,1]
USERS$COGNOME <- str_split(as.character(USERS$NAME), " ", n=2, simplify = TRUE)[,2]
USERS$POS[17]<-"external"
```

```{r}
grp = "ds-ac101"
usrs = filter(USERS, GROUP == grp) %>% 
  select("COGNOME","NOME","ID", "ROLE","POS") %>%
  arrange(ROLE, COGNOME)
kable(usrs, row.names=F)
```

# Projects

1. [Multi-information source Bayesian optimization via Augmented Gaussian Processes]()

    | | |
    |-|---|
    | PI | Antonio Candelieri |
    | TYPE |  |
    | KEYWORDS |  |
    | START/END | |
    | OUTPUT | |

2. [Automated Tiny Machine Learning]()

    | | |
    |-|---|
    | PI | Antonio Candelieri |
    | TYPE |  |
    | KEYWORDS |  |
    | START/END | |
    | OUTPUT | |

3. [Composition of kernel and acquisition functions for High Dimensional Bayesian Optimization]()

    | | |
    |-|---|
    | PI | Antonio Candelieri |
    | TYPE |  |
    | KEYWORDS |  |
    | START/END | |
    | OUTPUT | |

4. [Learning Optimal Control of Water Distribution Networks through Sequential Model-based Optimization]()

    | | |
    |-|---|
    | PI | Antonio Candelieri |
    | TYPE |  |
    | KEYWORDS |  |
    | START/END | |
    | OUTPUT | |