---
title: "ds-mb101"
output:
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r}
library(knitr)
library(dplyr)
library(ggpubr)
library(kableExtra)
library(rmarkdown)
library(stringr)
```

# Group

```{r}
load("USERS.RData")
USERS$NOME <- str_split(as.character(USERS$NAME), " ", simplify = TRUE)[,1]
USERS$COGNOME <- str_split(as.character(USERS$NAME), " ", n=2, simplify = TRUE)[,2]
USERS$POS[17]<-"external"
USERS$POS[19]<-"external"
```

```{r}
grp = "ds-mb101"
usrs = filter(USERS, GROUP == grp) %>% 
  select("COGNOME","NOME","ID","ROLE","POS","TUTOR") %>%
  arrange(ROLE, COGNOME)
kable(usrs, row.names=F)
```

# Projects

1. Hybrid approaches based on Bayesian Optimization and Deep Learning for self driving cars: steering wheel angle
prediction

    | | |
    |-|---|
    | PI |  Matteo Borrotti |
    | COLLABORATORS | Antonio Candelieri |
    | TYPE |  Research  |
    | KEYWORDS |  Deep Reinforcement Learning, Adversarial Learning, Hyperparameter optimization, Self driving cars |
    | START/END | 2020/01 - ongoing |
    | OUTPUT |  An hybrid approach based on Bayesian Optimization and Deep Learning for steering wheel angle prediction, working paper |

2. A study of Deep Reinforcement Learning approaches for automated criptocurrency trading and portfolio management

    | | |
    |-|---|
    | PI |  Matteo Borrotti |
    | COLLABORATORS | --- |
    | TYPE |  Research  |
    | KEYWORDS |  Deep Reinforcement Learning, Multi agent systems, Algorithmic trading, Portfolio management |
    | START/END | 2019/09 - on going   |
    | OUTPUT | A deep Q-learning portfolio management framework for the cryptocurrency market, working paper. Lucarelli, G., and Borrotti, M., A deep reinforcement learning approach for automated cryptocurrency trading, In J. MacIntyre et al. (Eds.), Artificial Intelligence Applications and Innovations , pp. 247–258, 2019 |

3. New regression models for constrained data

    | | |
    |-|---|
    | PI | Roberto Ascari  |
    | COLLABORATORS | |
    | TYPE |  |
    | KEYWORDS |  |
    | START/END |   |
    | OUTPUT |  |
    
4. Generalized species sampling model for nonparametric Bayesian inference

    | | |
    |-|---|
    | PI | Andrea Ongaro  |
    | COLLABORATORS | |
    | TYPE |  |
    | KEYWORDS |  |
    | START/END |   |
    | OUTPUT |  |
    
5. Stratified survival regression via Bayesian nonparametric mixtures

    | | |
    |-|---|
    | PI | Bernardo Nipoti |
    | COLLABORATORS | |
    | TYPE |  |
    | KEYWORDS |  |
    | START/END |   |
    | OUTPUT |  |
    
6. Approximate Bayesian inference for latent random partitions

    | | |
    |-|---|
    | PI | Riccardo Corradin |
    | COLLABORATORS | |
    | TYPE |  |
    | KEYWORDS |  |
    | START/END |   |
    | OUTPUT |  |

