---
title: "ds-mp101"
output:
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r}
library(knitr)
library(dplyr)
library(ggpubr)
library(kableExtra)
library(rmarkdown)
library(stringr)
```

# Group

```{r}
load("USERS.RData")
USERS$NOME <- str_split(as.character(USERS$NAME), " ", simplify = TRUE)[,1]
USERS$COGNOME <- str_split(as.character(USERS$NAME), " ", n=2, simplify = TRUE)[,2]
USERS$POS[17]<-"external"
USERS$POS[19]<-"external"
```

```{r}
grp = "ds-mp101"
usrs = filter(USERS, GROUP == grp) %>% 
  select("COGNOME","NOME","ID","ROLE","POS","TUTOR") %>%
  arrange(ROLE, COGNOME)
kable(usrs, row.names=F)
```

# Projects

1. Estimation of high dimensional multivariate stochastic volatility
models

    | | |
    |-|---|
    | PI | Matteo Pelagatti |
      | COLLABORATORS | Giacomo Sbrana (NEOMA Business School) |
    | TYPE | Scientific research |
    | KEYWORDS | Finance, high dimensional data, portfolio management, Kalman filter |
    | START/END | 2018-2019 |
    | OUTPUT | Journal Article |


    
2. Measuring dependence between random variables and auto-dependence
of time series

    | | |
    |-|---|
    | PI | Matteo Pelagatti |
    | COLLABORATORS |  |
    | TYPE |  |
    | KEYWORDS | |
    | START/END | |
    | OUTPUT | |
